CS182: NBA Scheduler

### 2015-12-09 paper.tex
write schedule command line tool

	\section{Repository}
	We felt it unnecessary to submit the code to Canvas as there are quite a few files. Our github repository is located at \url{https://github.com/chuckyouliu/NBA_Scheduler}. Basic description of important files:

	\begin{itemize}
		\item ILP\_formulation.py - As name suggests the ILP code is located here
		\item datagen.py - Formulation of the date indices
		\item organization.py - Classes corresponding to team/division/league/conference
		\item domain.py - Classes corresponding to the CSP's with functions calculating the heuristics
		\item constraint.py - Functions associated with forward checking, used by classes in domain.py
		\item scheduler.py - Main class for solving schedule, creates variables/domains that are fed into domain.py
	\end{itemize}
	Our results of an example schedule are stored in the json files. We created a simple command line tool to read from the json files by typing for example:
	\begin{center}
		python read\_schedule.py -n 5 -t Knicks,Celtics
	\end{center}
	This will output the first 5 games of the schedule for Knicks and Celtics. Use -h to see the list of possible teams.

>>>>

	\section{Running the Repository}
	We felt it unnecessary to submit the code to Canvas as there are quite a few files. Our github repository is located at \url{https://github.com/chuckyouliu/NBA_Scheduler}. Basic description of important files:

	\begin{itemize}
		\item ILP\_formulation.py - As name suggests the ILP code is located here
		\item datagen.py - Formulation of the date indices
		\item organization.py - Classes corresponding to team/division/league/conference
		\item domain.py - Classes corresponding to the CSP's with functions calculating the heuristics
		\item constraint.py - Functions associated with forward checking, used by classes in domain.py
		\item scheduler.py - Main class for solving schedule, creates variables/domains that are fed into domain.py
	\end{itemize}
	To create a schedule, you can use a command line tool that we've written called write\_schedule. An example command would be:
	\begin{center}
		python write\_schedule.py -m True -d True -y 2016
	\end{center}
	This would create a schedule for the year 2016. The -d stands for debug, so debug outputs would be shown, and the -m stands for if you'd like to use an already existing Matchups.json file, so only create new home/aways and dates not new matchups. Setting that to False would create an entirely new schedule with new matchups.
	Our results of an example schedule are stored in the json files. We created a simple command line tool to read from the json files by typing for example:
	\begin{center}
		python read\_schedule.py -n 5 -t Knicks,Celtics
	\end{center}
	This will output the first 5 games of the schedule for Knicks and Celtics. Use -h to see the list of possible teams.

	\section{Work Distribution}
	\begin{itemize}
	\item Data Generation - Charles created the structure of the league as well as the initial data generation class. As the project progressed changes were made by all members.
	\item ILP - Sam and Abhishek worked on the initial matchups problem. From there, Abhishek took the lead on solving home/away's and dates as well as moving to the faster GUROBI.
	\item CSP - Charles created the general structure of the scheduler/domain/constraint files and the sub-CSP problems. From there the more involved work (heuristics, testing) were split as follows:
		\begin{itemize}
			\item Matchups heuristics - Charles
			\item Home/Aways heuristics - Charles and Sam pair coded
			\item Dates/UCS - primarily Sam with some input on cost functions from Charles
		\end{itemize}
	\end{itemize}
